Mountaineering: Be lucky first, prepared second

### 2024-12-14 paper/paper.qmd
update paper

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(kableExtra)
library(readr)
library(dplyr)
library(arrow)
library(here)
library(ggplot2)
library(arkhe)
library(modelsummary)
library(kableExtra)

@@

expeditions$success <- expeditions$termination_reason %in% c("Success (main peak)", "Success (subpeak)")
success_rate <- expeditions |>
  group_by(members)|>
  summarize(success_rate = mean(success))
ggplot(success_rate, aes(x = members, y = success_rate)) +
  geom_line(color = "blue") + # Line plot
  geom_point(color = "red") + # Points to emphasize values
  labs(
    title = "Success Rate by Members",
    x = "Number of Members",
    y = "Success Rate"
  ) +
  theme_minimal()
```

@@

>>>>

```{r}
#| include: falsex
#| warning: false
#| message: false
library(tidyverse)
library(knitr)
library(kableExtra)
library(readr)
library(dplyr)
library(arrow)
library(here)
library(ggplot2)
library(arkhe)
library(modelsummary)
library(kableExtra)

@@

success_rate <- expeditions |>
  group_by(members)|>
  summarize(success_rate = mean(success))
ggplot(success_rate, aes(x = members, y = success_rate)) +
  geom_line(color = "blue") + # Line plot
  geom_point(color = "red") + # Points to emphasize values
  labs(
    title = "Success Rate by Members",
    x = "Number of Members",
    y = "Success Rate"
  ) +
  theme_minimal()
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-hired
#| fig-cap: "Distribution of Himialayan peaks, mountains recorded are centered around 6200 M above sea level.."

ggplot(expeditions, aes(hired_staff))+
  geom_histogram(
    binwidth = 1
  )
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-hired
#| fig-cap: "Distribution of Himialayan peaks, mountains recorded are centered around 6200 M above sea level.."
success_rate <- expeditions |>
  group_by(hired_staff)|>
  summarize(success_rate = mean(success))
ggplot(success_rate, aes(x = hired_staff, y = success_rate)) +
  geom_line(color = "blue") + # Line plot
  geom_point(color = "red") + # Points to emphasize values
  labs(
    title = "Success Rate by Members",
    x = "Number of Members",
    y = "Success Rate"
  ) +
  theme_minimal()
```

@@

average age

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-ssdistribution
#| fig-cap: "Distribution of Himialayan peaks, mountains recorded are centered around 6200 M above sea level.."

ggplot(expeditions, aes(average_age)) +
  geom_histogram()
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-ssdistribution
#| fig-cap: "Distribution of Himialayan peaks, mountains recorded are centered around 6200 M above sea level.."
success_by_age <- expeditions |>
  group_by(age_range) |>
  summarize(success_rate = mean(success, na.rm = TRUE))
ggplot(success_by_age,aes( x = age_range, y = success_rate))+
  geom_bar(stat = 'identity')

```
